Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
wordings

The experimental evaluation in section~\ref{experimental-results} shows
a very positive evaluation of \tool over a diverse set of real-world
benchmarks. Nevertheless, the set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios.

Furthermore, our algorithm to select suitable FWL word widths to model
plant behaviour employs a heuristic based on user-provided controller
word width specifications. Given the encouraging results of our benchmarks,
this heuristic appears to be strong enough for the current benchmark set,
but this may not hold in general. Further experiments towards determining
suitable plant FWL configurations may thus be necessary in future work.

>>>>

We report a favourable assessment of \tool over a diverse set of real-world
benchmarks.  Nevertheless, the set of benchmarks is limited within the scope
of this paper and \tool's performance may not generalise to other
application scenarios.  This can be addressed by expanding the benchmark set
in future experiments.

Furthermore, our algorithm for selecting the fixed-point precision to model
plant behaviour employs a heuristic based on user-provided controller
word-width specifications.  Given the encouraging results of our benchmarks,
this heuristic appears to be strong enough for the current benchmark set,
but this may not generalise.  Further experiments towards determining
suitable plant FWL configurations may thus be necessary in future work.

Finally, the experimental results we obtained using \tool for stability
properties may not generalise to other properties.  The inductive nature of
the two-stage back-end of \tool increases performance significantly compared
to the one-stage back-end, but this performance benefit introduced by CEGIS'
inductive generalisations may not be observed for other controller
properties.  Additional experiments are necessary to confirm that the
performance of our inductive synthesis approach can be leveraged in those
scenarios as well.
